### 2021-05-06 doc/thesis/chapters/dsp.tex
first graphic with draw.io

\includepicture [0.6] [0] {Frequency discriminator block diagram \cite{ref_fig_freq_discriminator}.} {bd_freq_discriminator} {img/discrimination_method_bd1.jpg}

>>>>

\includepicture [0.7] [0] {Frequency discriminator block diagram \cite{ref_fig_freq_discriminator}.} {bd_freq_discriminator} {img/bd_freq_discriminator}
